%*******************************************************
% Abstract
%*******************************************************
%\renewcommand{\abstractname}{Abstract}
\pdfbookmark[1]{Abstract}{Abstract}

\chapter*{Abstract}
\selectlanguage{american} % american ngerman
Designing software architectures to meet the latest requirements is a complex and difficult task. One possibility to design distributed software is offered by the actor-model, which is discussed in detail in the context of this work. TheActor-Model was designed as a programming model for parallel software development \citep{hewitt1973session}. The characteristics of this model, such as message orientation or data isolation, are ideally suited as a basis for distributed software architectures. \\
In order to develop software applications, the architecture of the software should have various elementary properties in order to meet current requirements. Among other things, the Reactive Manifesto (\cite{reactiveManifesto}) provides a basis for a modern software architecture. 
A frequent requirement of business applications is the consistency and durability of the processed data. The distribution of such systems has some problems, such as the CAP theorem \citep{gilbertPerspectiveCAPTheorem2012}. \\
In the scope of this master thesis, based on the theoretical examination of the three main topics actor-model, transaction-systems and distributed-systems, a set of requirements was created which summarizes the typical fields of application of these three topics. The fictional flight booking system \textit{TyrolSky} is used as an application example. The implementation is focused on distributing the entire application without allowing data inconsistencies in the application-specific data. \\
The implementation is based on the actor-framwork \textit{Akka.net} (\cite{Akka.netCommunityAkka.NETDocumentation}). This implemented solution offers four different components, all of which are instantiated several times. The software automatically distributes the data within these components.
The work showed that the actor-model is suitable for the development of distributed systems. Designing distributed systems with transaction data remains a challenge, but the Actor-Model can be used to support easier handling of this.


\cleardoublepage
\selectlanguage{ngerman} % american ngerman